Industrial Applications of CFD

### 2011-03-07 MSTE_methodology.tex
with figures and cfd templates/style

@@

@@

%\abstract{
%  This file is an example \LaTeX file for submission to CFD2011.  A
%  limit of 10 pages applies.
%}
%\keywords{
%  CFD, hydrodynamics, chemical reactors
%}
%\normalfont\normalsize
%
%
%
%%\section{Nomenclature}
%A complete list of symbols used, with dimensions, is required.
%%the nomenclature needs to be entered into the file ExampleFile.nls
%\printnomenclature[0.7cm]  
%\vskip .1em
%
%
%\section{Introduction}
%The introduction goes here.
%
%
%\newpage
%
%
%
%\section{Model Description}
%You should give a thorough description of your model.
%\vspace{4cm}
%\subsection{Example of Subheading}
%Here is how to produce a numbered equation under a second level
%heading \cite{James1988}.
%\vspace{2cm}\\
%\emph{Continuity equation}
%\begin{equation}
%  \frac{\partial \rho_G}{\partial t}+\nabla\left(\rho_G\mathbf
%    u\right)=0
%\end{equation}
%
%\subsubsection*{Example of Sub-subheading}
%This is how \cite{Luke1988} produced an unnumbered equation under a
%third level heading.
%\begin{equation}
%  \mathbf J=\sigma(\mathbf E+\mathbf u\times\mathbf B)
%\end{equation}
%\newpage
%
%\InsFig{figure}{Schematic diagram of geometry.}{label1}
%\InsFigRot{figure}{Rotated schematic diagram of geometry.}{label2}
%
%
%\section{Results}
%The results of using the \LaTeX template is a great looking paper.
%In Figures \ref{fig:label1} and \ref{fig:label2} it can be seen how figures are easily included.
%In Table \ref{tab:label} it is seen how we can include a table.
%The table is constructed in the file table.tex, where also the table caption and label are defined.
%
%
%\newpage
%\InsTab{Table}
%
%
%\section{Conclusion}
%The conclusions are:
%\begin{enumerate}
%  \item Trondheim is a nice city.
%  \item CFD is great fun, and useful too.
%\end{enumerate}
%
\newpage
%
%
%% %---------------------------
%% %BIBLIOGRAPHY
%% %---------------------------
%The bibliography is created using BiBTeX
\bibliographystyle{CFD2011}
\bibliography{MSTE}

>>>>

\newcommand{\TODO}[1]{TODO: #1 \\}

@@

\section{Introduction}

\TODO{    * Describe traditional approaches for porous media problems}
\TODO{     * Introduce the concept of the topology of porous media and define the pore size distribution. (esto es nuevo?) NO, tengo referencias de hace unos anios.}
\TODO{     * Describe how porous media problems can be affected by the pore scale (capillarity, heterogeneous reactions, permeability and channelling)}
\TODO{     * Introduce the MSTE}
\TODO{     * Comment on the challenges for solving the MSTE}
\TODO{     * Compare the MSTE with other internal variable problems and suggest LSQ as a possibility.}
\TODO{     * Introduce LSQ}

\TODO{           o State the scope of the article.}

\TODO{     * State clearly that the paper will not address how to find the MSTE kernels. No comparison with experiments is given.}
\TODO{     * Suitability of the method will be shown by the manufactured solution method.}
\TODO{     * Mention the assumptions of steady state, etc, for the present analysis.}

\TODO{     * This paper proposes and explains how to solve MSTE with LSQ.}

\section{Model}

\section{    * Explain the porosity  distribution concept}
\section{    * Explain the permeability, advective velocity per pore scale.}
\section{    * Explain the redistribution}
\section{    * Explain the meaning of the cumulative distribution functions}
\section{    * Explain MSTE}
\section{    * Point out challenges for solving the equation}

@@

\section{Numerical Example}

\TODO{[REESCRIBIR ECUACIONES]}

\TODO{Mention implementation details (polynomials and quadratures used, number of points, solver, etc.).  ouch... }

\TODO{Explain and show q, epsilon and h. and BCs}

\InsFig{profiles}{Left column: porosity distribution (top) and cumulative porosity distribution (bottom). Middle column: discharge distribution (top) and cumulative discharge distribution (bottom). Right column: velocity per channel (top), and 1-metre residence time (bottom)}{profiles}

\TODO{Describe what case could be described with this simplified model.}

\TODO{Show solution (phi) and S.}

\InsFig{solution}{Solution}{solution}
\InsFig{source}{Source}{source}

\TODO{Explain what is happening with phi and S in each scale, and the mixing by h.}

\TODO{Show and comment on convergence plot}

\InsFig{convergence}{Convergence plot}{convergence}

\section{Conclusion}

\TODO{Contribution of this paper:}

\TODO{    * This paper proposes and explains how to solve MSTE with LSQ.}
\TODO{    * Shows that LSQ solves the MSTE with exponential convergence.}

\TODO{mas despues que tengamos todas las figuras}

%\abstract{
%  This file is an example \LaTeX file for submission to CFD2011.  A
%  limit of 10 pages applies.
%}
%\keywords{
%  CFD, hydrodynamics, chemical reactors
%}
%\normalfont\normalsize
%
%
%
%%\section{Nomenclature}
%A complete list of symbols used, with dimensions, is required.
%%the nomenclature needs to be entered into the file ExampleFile.nls
%\printnomenclature[0.7cm]  
%\vskip .1em
%
%
%\section{Introduction}
%The introduction goes here.
%
%
%\newpage
%
%
%
%\section{Model Description}
%You should give a thorough description of your model.
%\vspace{4cm}
%\subsection{Example of Subheading}
%Here is how to produce a numbered equation under a second level
%heading \cite{James1988}.
%\vspace{2cm}\\
%\emph{Continuity equation}
%\begin{equation}
%  \frac{\partial \rho_G}{\partial t}+\nabla\left(\rho_G\mathbf
%    u\right)=0
%\end{equation}
%
%\subsubsection*{Example of Sub-subheading}
%This is how \cite{Luke1988} produced an unnumbered equation under a
%third level heading.
%\begin{equation}
%  \mathbf J=\sigma(\mathbf E+\mathbf u\times\mathbf B)
%\end{equation}
%\newpage
%

%\InsFig{figure}{Schematic diagram of geometry.}{label1}
%\InsFigRot{figure}{Rotated schematic diagram of geometry.}{label2}
%
%
%\section{Results}
%The results of using the \LaTeX template is a great looking paper.
%In Figures \ref{fig:label1} and \ref{fig:label2} it can be seen how figures are easily included.
%In Table \ref{tab:label} it is seen how we can include a table.
%The table is constructed in the file table.tex, where also the table caption and label are defined.
%
%
%\newpage
%\InsTab{Table}
%
%
%\section{Conclusion}
%The conclusions are:
%\begin{enumerate}
%  \item Trondheim is a nice city.
%  \item CFD is great fun, and useful too.
%\end{enumerate}
%
\newpage
%
%
%% %---------------------------
%% %BIBLIOGRAPHY
%% %---------------------------
%The bibliography is created using BiBTeX
\bibliographystyle{CFD2011}
\bibliography{MSTE}
